---
title: "Plotly and Flexboard"
author: "Jingyi Yao"
date: "`r Sys.Date()`"
output: html_document
---

```{r,message=FALSE}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```

## NYC Airbnb Data
```{r}
data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>%
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>%
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500)

```

## 1. Plotly Scatterplot

#### `str_c("text",variable)` combines text and the variable, using comma to connect
#### `type = "scatter"` draws a scatter plot
#### `mode = "markers"` draws the point like `geom_point`  remember the s
#### `mode = "lines"` draws lines like `geom_line`         remember the s
#### `alpha` sets the transparency

```{r}
nyc_airbnb %>%
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) %>% 
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)

```



## 2. Plotly  Boxplot

#### boxplot has no `mode` to choose from
#### `type = "box"` to draw box plots
#### By clicking on the groups, we can add or remove them
#### `fct_reorder(vector1,vector2,.desc=F)` order v1 by v2, by default ascending

```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")

```



## 3. Plotly barchart

```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")

```


```{r}


```


```{r}


```